---
title: "Main Figures"
author: "Sean Maden"
date: "10/8/2020"
output: html_document
---

```{r setup, include=FALSE}
library(recountmethylationManuscriptSupplement)
pkgname <- "recountmethylationManuscriptSupplement"
scripts.dir <- system.file("scripts", package = pkgname)

library(ggplot2)
library(gridExtra)
library(data.table)

knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Figure 1

Some details about the platforms of interest are as follows:

```{r, echo = FALSE, eval = TRUE}
lid <- list(c('GPL13534','HM450K','2011','May 2011'),
            c('GPL21145', 'EPIC','2015','Nov. 2015'),
            c('GPL8490', 'HM27K','2009','Apr. 2009')
)
df <- as.data.frame(do.call(rbind, lid))
colnames(df) <- c("platform_id", "platform_name", 
                  "release_year", "release_month")
knitr::kable(df)
```

## 1A Available GEO samples (GSM IDs) by year, platform, and type

Obtain sample (GSM IDs) and study (GSE IDs) summaries from queries to GEO 
with queries to Entrez utilities. With 
[Entrez utilities](https://www.ncbi.nlm.nih.gov/books/NBK179288/) installed, navigate 
to the directory with the script "eqplot.py" and run:

```
python3 eqplot.py
```

This will cause data queries to the GEO servers, and result in the creation 
of several new files, "gsmyeardata", "gsmidatyrdata", "gseyeardata", and 
"gseidatyrdata". Finally, run the script "fig1a.R" to make the plot.

```{r, eval = TRUE}
script.name <- "fig1a.R"
source(file.path(scripts.dir, script.name))
fig1a
```

## 1B

See data analyses vignette in [`recountmethylation`](https://bioconductor.org/packages/devel/bioc/vignettes/recountmethylation/inst/doc/recountmethylation_data_analyses.pdf)

# Figure 2

## 2A BeadArray control outcomes

Source the script "fig2a.R". This creates control outcomes from BeadArray signals
in Table S2, then generates the plot object.

```{r, eval = TRUE}
script.name <- "fig2a.R"
source(file.path(scripts.dir, script.name))
fig2a
```

## 2B Quality signals, by storage condition

See data analyses vignette in [`recountmethylation`](https://bioconductor.org/packages/devel/bioc/vignettes/recountmethylation/inst/doc/recountmethylation_data_analyses.pdf)

## 2C Percent BeadArray control failure, by storage condition

## 2D Study-level quality assessments

```{r, eval = TRUE}
script.name <- "fig2d.R"
source(file.path(scripts.dir, script.name))
draw(hmlist, row_title = paste0("Study ID (N = ", 
                                length(gsesize.subset),")"), 
     column_title = "Sub-threshold Frequency", 
     heatmap_legend_side = "right", annotation_legend_side = "right")
```

# Figure 3 PCA of autosomal DNAm

Details including sample identification, analyses, and results summaries are detailed in 
the script `pca_fig3.R`. This script generates the files contained in 
`r system.file("extdata", "pcadata", package = pkgname)`, which are used below to 
generate the main plots.

## 3A

Run the following to generate the scatterplot of the top two components from PCA of 
all samples. Red points are noncancer blood, purple points are leukemia samples.

```{r, eval = TRUE}
script.name <- "fig3a.R"
source(file.path(scripts.dir, script.name))
fig3a
```

## 3B

Run the following to generate the scatterplot of the top two components from PCA of 
all samples except blood or leukemias. Blue points are noncancer brain, dark cyan points are 
brain tumors.

```{r, eval = TRUE}
script.name <- "fig3b.R"
source(file.path(scripts.dir, script.name))
fig3b
```

## 3C

Run the following to generate the scatterplot of the top two components from PCA of 
7 noncancer tissues: sperm (blue); adipose (dark red); blood (red); brain (purple); buccal (orange); nasal (light green); and liver (dark green).

```{r, eval = TRUE}
script.name <- "fig3c.R"
source(file.path(scripts.dir, script.name))
fig3c
```

## 3D

Run the following to generate the scatterplot of the top two components from PCA of 
6 noncancer tissues: adipose (dark red); blood (red); brain (purple); buccal (orange); nasal (light green); and liver (dark green).

```{r, eval = TRUE}
script.name <- "fig3d.R"
source(file.path(scripts.dir, script.name))
fig3d
```

# Figure 4 DNAm variability in noncancer tissues

For analysis details, see also the data analyses vignette in [`recountmethylation`](https://bioconductor.org/packages/devel/bioc/vignettes/recountmethylation/inst/doc/recountmethylation_data_analyses.pdf) 

## 4A

Violin plots of 14,000 high variance probes

```{r}
script.name <- "fig4a.R"
source(file.path(scripts.dir, script.name))
fig4a
```

## 4B

Stacked barplots of probe region summaries

```{r}
script.name <- "fig4b.R"
source(file.path(scripts.dir, script.name))
fig4b
```
